### 2016-11-23 dissertation/normal.tex
dissertation v2_part reacha update 1

\chapter{Functional Verification of Sequential Normal Basis Multiplier}
\label{ch:normal}
In order to utilize our traversal algorithm, it is necessary to find out
a sort of suitable circuit benchmarks which is easy to compute its
Gr\"obner basis (GB). From the work of Lv et al. \cite{lv_dissertation},
we learn that arithmetic circuits in Galois field (GF) is
convertible to an ideal of circuit polynomials, and the 
ideal generators form a GB themselves when applying reverse topological
term order. Furthermore, according to the work of Pruss et al.
\cite{tim_dissertation}, with a limited computation complexity,
we can abstract the word-level signature of an arithmetic 
component working in GF. Thus, we consider the possibility 
of applying our traversal algorithm on sequential Galois
field circuits. In each frame, we can use the techniques 
from \cite{tim_dissertation} to abstract the word-level
signature of the combinational logic, which corresponds
to the transition function in our traversal algorithm.
As a result, we manage to find a type of sequential GF multiplier
which we can apply our traversal algorithm to actually 
verify its functional correctness.

\section{Motivation}
\label{sec:normal_motiv}
From the preliminaries (Chapter \ref{ch:prelim}) about FSMs, we learn that the
Moore machine does not rely on inputs for state transitions. 
As depicted in Figure \ref{fig:Moore}(a), a typical Moore machine implementation
consists of combinational logic component and register files, where
$r_0,\dots,r_k$ are present state (PS) variables 
standing for state inputs (SI), and $r_0',\dots,r_k'$ are next state (NS) variables standing for
state outputs (SO). Figure \ref{fig:Moore}(b) shows the state transition graph (STG) of 
a Moore machine with $k+1$ distinct states. We notice that it forms a simple chain,
with $k$ consecutive transitions the machine reaches final state $R_k$.

>>>>

\chapter{Functional Verification of Sequential Normal Basis Multiplier}
\label{ch:normal}
In order to utilize our traversal algorithm, it is necessary to find out
a sort of suitable circuit benchmarks which is easy to compute its
Gr\"obner basis (GB). From the work of {\it Lv} \cite{lv:phd},
we learn that arithmetic circuits in Galois field (GF) is
convertible to an ideal of circuit polynomials, and the 
ideal generators form a GB themselves when applying reverse topological
term order. Furthermore, according to the work of {\it Pruss et al.}
\cite{pruss:tcad15}, with a limited computation complexity,
we can abstract the word-level signature of an arithmetic 
component working in GF. Thus, we consider the possibility 
of applying our traversal algorithm on sequential Galois
field circuits. In each frame, we can use the techniques 
from \cite{pruss:tcad15} to abstract the word-level
signature of the combinational logic, which corresponds
to the transition function in our traversal algorithm.
As a result, we manage to find a type of sequential GF multiplier
which we can apply our traversal algorithm to actually 
verify its functional correctness.

\section{Motivation}
\label{sec:normal_motiv}
From the preliminaries about FSMs in section \ref{sec:reach}, we learn that the
Moore machine does not rely on inputs for state transitions. 
As depicted in Figure \ref{fig:Moore}(a), a typical Moore machine implementation
consists of combinational logic component and register files, where
$r_0,\dots,r_k$ are present state (PS) variables 
standing for state inputs (SI), and $r_0',\dots,r_k'$ are next state (NS) variables standing for
state outputs (SO). Figure \ref{fig:Moore}(b) shows the state transition graph (STG) of 
a Moore machine with $k+1$ distinct states. We notice that it forms a simple chain,
with $k$ consecutive transitions the machine reaches final state $R_k$.

### 2016-11-23 dissertation/prelim_basis.tex
dissertation v2_part reacha update 1

\chapter{Gr\"ober Basis and Algebraic Geometry} \label{ch:ideals}
This chapter reviews fundamental concepts of commutative and 
computer algebra which are used in this work. 
Specifically, this chapter covers monomial ordering, polynomial ideals and 
varieties, and the computation of \Grobner bases.
It also overviews elimination theory as well as Hilbert's Nullstellensatz 
theorems and how
they apply to Galois fields. The results of these theorems are used in polynomial
abstraction and formal verification of Galois field circuits and 
are discussed 
in subsequent chapters. The material of this chapter is
mostly referred from the textbooks \cite{ideals:book} \cite{gb_book} and 
previous work by {\it Lv} \cite{lv:phd} as well as {\it Pruss} \cite{pruss:tcad15}

@@

\Grobner basis computation depends on the $Spoly$ computation, which in turn 
depends on the leading terms of polynomials. Thus, different monomial 
orderings can result in different \Grobner basis computations for the 
same ideal. Computation using a degrevlex ordering tends to be least 
difficult, while lex ordering tends to be computationally complex. However, 
lex ordering used in the computation of \Grobner basis is an {\bf elimination
ordering}; that is, the polynomials contained in the resulting \Grobner basis
have continuously eliminated variables in the ordering. This is the topic of 
elimination theory, which is described in the following section.

>>>>

\chapter{Gr\"ober Basis and Algebraic Geometry} \label{ch:ideals}
This chapter reviews fundamental concepts of commutative and 
computer algebra which are used in this work. 
Specifically, this chapter covers monomial ordering, polynomial ideals and 
varieties, and the computation of \Grobner bases.
It also overviews elimination theory as well as Hilbert's Nullstellensatz 
theorems and how
they apply to Galois fields. The results of these theorems are used in polynomial
abstraction and formal verification of Galois field circuits and 
are discussed 
in subsequent chapters. The material of this chapter is
mostly referred from the textbooks \cite{ideals:book} \cite{gb_book} and 
previous work by {\it Lv} \cite{lv:phd} as well as {\it Pruss} \cite{pruss:tcad15}.

@@

\Grobner basis computation depends on the $Spoly$ computation, which in turn 
depends on the leading terms of polynomials. Thus, different monomial 
orderings can result in different \Grobner basis computations for the 
same ideal. Computation using a degrevlex ordering tends to be least 
difficult, while lex ordering tends to be computationally complex. However, 
lex ordering used in the computation of \Grobner basis is an {\bf elimination
ordering}; that is, the polynomials contained in the resulting \Grobner basis
have continuously eliminated variables in the ordering. This is the topic of 
elimination theory, which is described in the following sections as well as 
its theoretic basis -- the Nullstellensatz theory.
